An examination of the accessibility implications of a pilot COVID-19 vaccination program in Hamilton, Ontario

### 2021-04-07 Accessibility-Vaccination-Sites-Hamilton/Accessibility-Vaccination-Sites-Hamilton.Rmd
v1 Calculated person-hours of travel savings by mode

@@

@@

>>>>

```{r weighted-travel-time-by-mode-baseline, include=FALSE}
# Baseline analysis (PILOT LOCATIONS ONLY)
## Bind the three tables and label them by mode:
min_ttm_mode_baseline <- rbind(data.frame(min_ttm_car, Mode = "Car"),
                               data.frame(min_ttm_transit, Mode = "Transit"),
                               data.frame(min_ttm_walk, Mode = "Walking"))
```

@@

```{r weighted-travel-time-by-mode, include=FALSE}
# Baseline analysis (PILOT LOCATIONS ONLY)
## Bind the three tables and label them by mode:
min_ttm_mode <- rbind(data.frame(min_ttm_car, Mode = "Car"),
                      data.frame(min_ttm_transit, Mode = "Transit"),
                      data.frame(min_ttm_walk, Mode = "Walking"))
```

@@

```{r comparison-travel-time-by-mode, echo=FALSE}
# Comparison of weighted travel times by mode between pilot and scenario
min_ttm_mode_baseline %>%
  group_by(Mode) %>%
  summarize(pht_mode = sum(Population * weighted_travel_time/60),
            .groups = "drop")

min_ttm_mode %>%
  group_by(Mode) %>%
  summarize(pht_mode = sum(Population * weighted_travel_time/60),
            .groups = "drop")
```
